Addressing selection bias and measurement error in COVID-19 case count data using auxiliary information

### 2023-01-10 write-up/letters/cover letter-covid.tex
Finishing paper once and for all...ha

Kindly find enclosed the revised version of the manuscript number AOAS2006-048 titled ``Addressing selection bias and measurement error in COVID-19 case count data using auxiliary information.''  We are happy that the two reviewers, associate editor, and editor have all found the revision much improved. We have revised the article to address the few remaining concerns that one of the reviewers raised but are glad that they ``appreciate the paper and [are] very supportive of the pragmatic approach.''  We have edited the remark, performed a sensitivy analysis to assess sensitivity due to potential confounding, and adjusted the figures to assist in comprehension.

We continue to believe the work presents an important advance in how researchers should think about addressing time-varying selection bias and measurement error to better understanding the COVID-19 pandemic trajectory. Attached please find a detailed response to the referee outlining how the changes to the manuscript address the concerns raised in their report.

>>>>

Kindly find enclosed the revised version of the manuscript number AOAS2006-048 titled ``Addressing selection bias and measurement error in COVID-19 case count data using auxiliary information.''  We are happy that the revised manuscript was found to address the remaining concerns raised by the reviewers. At the Editor's request, we have shortened the article to 26 pages without references and included 5 figures.  The main paper still retains all of the main points while the supplement contains important but secondary analyses and discussions that were removed from the main paper in this editing process.

We continue to believe the work presents an important advance in how researchers should think about addressing time-varying selection bias and measurement error to better understanding the COVID-19 pandemic trajectory.
